Manuscript 2: Child Health Outcomes

### 2020-11-23 papertwo_child_health.Rmd
Updating decision to drop adult mental health outcomes from child paper.

And now modeling for adult experiences:
```{r, echo=TRUE, message=FALSE, warning=FALSE}
##Assembling child health indicators:
child_sum <- group_by(child_adult, unique_id) %>% summarise(child_screen = as.numeric(sum(as.numeric(gettested)-1, na.rm=TRUE) > 0), child_symps = sum(overall_symp), child_bll = as.numeric(sum(as.numeric(elevbll)-1, na.rm=TRUE) > 0), child_rash = as.numeric(sum(as.numeric(rash)-1, na.rm=TRUE) > 0), child_hair = as.numeric(sum(as.numeric(hair)-1, na.rm=TRUE) > 0), child_learning = as.numeric(sum(as.numeric(learn)-1, na.rm=TRUE) > 0), child_hyper = as.numeric(sum(as.numeric(hyper)-1, na.rm=TRUE) > 0), child_irritable = as.numeric(sum(as.numeric(irritable)-1, na.rm=TRUE) > 0))

>>>>

And now modeling for adult experiences (dropped from paper 2; will be used elsewhere:
```{r, echo=TRUE, message=FALSE, warning=FALSE}
##Assembling child health indicators:
child_sum <- group_by(child_adult, unique_id) %>% summarise(child_screen = as.numeric(sum(as.numeric(gettested)-1, na.rm=TRUE) > 0), child_symps = sum(overall_symp), child_bll = as.numeric(sum(as.numeric(elevbll)-1, na.rm=TRUE) > 0), child_rash = as.numeric(sum(as.numeric(rash)-1, na.rm=TRUE) > 0), child_hair = as.numeric(sum(as.numeric(hair)-1, na.rm=TRUE) > 0), child_learning = as.numeric(sum(as.numeric(learn)-1, na.rm=TRUE) > 0), child_hyper = as.numeric(sum(as.numeric(hyper)-1, na.rm=TRUE) > 0), child_irritable = as.numeric(sum(as.numeric(irritable)-1, na.rm=TRUE) > 0))
